Imputation of incomplete multilevel data

### 2024-02-29 manuscript.qmd
Add outline case study

>>>>

# Case study

1. Load the data, make sure the variables are correctly formatted (e.g. numeric clustering variable)
2. Explore the missingness
2. Fix any cluster-level missingness determinately (note that `2l.only` methods do not work if there are inconsistencies, fix those first!)
2. Re-evaluate the missingness
3. Explore bivariate relations and associations with missingness indicators
4. Determine the imputation methods
5. Create the predictor matrix
6. Impute the incomplete data
7. Evaluate convergence
8. Evaluate imputations
9. Analyse and pool
10. For further multilevel model building, AICs could be pooled, how?
